A Linear Solution of the Linearity Challenge

### 2025-12-28 paper/Examples.lagda.tex
tuning

    However, now in each constructor we have to make a distinction between the
    first arrow \AgdaFunction{⇒} and the following magic wands \AgdaFunction{─∗}
    to account for the appropriate amount of context splittings. We found this
    formulation of the constructors harder to explain and motivate in
    \Cref{sec:process-agda}.
    %
    In the end, none of the alternative definitions of the data type
    \AgdaDatatype{Proc} was fully satisfactory and we preferred the cleanest and
    most readable version at the expense of additional clutter in this section.
    %
    \eoe
\end{remark}

>>>>

    However, now we have to make a distinction between the first arrow
    \AgdaFunction{⇒} and the following magic wands to account for the
    appropriate amount of context splittings. We found this formulation of the
    constructors harder to explain and motivate in \Cref{sec:process-agda}.
    %
    Since none of the alternative definitions of \AgdaDatatype{Proc} was fully
    satisfactory, we preferred the cleanest and most readable version of the
    data type at the expense of additional clutter in this section.
    %
    \eoe
\end{remark}
